Untitled

### 2019-08-01 Manuscript_draft/Tables_and_figures.Rmd
Edits of organization

**Table 2**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")
Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
Cross <- cross
Self <- self
Natural_selfing <- nat_self
Apomixis <- apo
table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
kable(table, format="markdown", caption= "Perecentage of seeds produced per ovule for the ten species used in the experiment. The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
",longtable = TRUE)
```

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
knitr::include_graphics('images/phylo_image.png')
```
**Figure 1**
\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
load("r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

@@

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5}
load("Data/family_cor.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

p1 <- ggscatter(sola, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")

p2<- ggscatter(a, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) All families")
grid.arrange(p1, p2, nrow = 1, ncol=2)

```
**Figure 7**

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
load("pollen_ratio.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

>>>>

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
knitr::include_graphics('images/phylo_image.png')
```
**Figure 1**
\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
load("Data/r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

@@

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
load("Data/pollen_ratio.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)
